Cartograms with Dynamic Features

### 2022-08-11 paper/section/main.tex
draft: evaluation

\begin{algorithm}[tb!]
    \caption{Procedure to adjust river positions, remove node overlap and prevent nodes from crossing rivers.}\label{alg:UpdateLayout}
    \textbf{Global variables:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs with the following properties: \\
    \-\hspace{1em}  \textcolor{blue}{$\nodeListCross \gets $ the number of $ \node $ in $ \nodeList $ that crosses a river} \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    \textcolor{blue}{ $ \riverList \gets $ a list of $ \river $ representing river features} \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

@@

    \begin{algorithmic}[1]
        \Procedure{UpdateLayout}{}
        \While{$ \nodeSize < \nodeSizeMax $}
            \State \textcolor{blue}{$ \nodeListCross \gets 1 $ \Comment{Trigger the while loop}}
            \While{$ \nodeListCross > 0 $}

                \State $ \nodeListCross \gets 0 $
                \State $ \nodeList \gets $ RemoveOverlap ($ \nodeList $)
                \color{blue}
                \State \Call{TranslateRiver}{$ \nodeList $}
                \State $\nodeListCross \gets $ \Call{TranslateNode}{$ \nodeList $}

@@

\begin{algorithm}[tb!]
    \caption{Procedure to translate rivers.}\label{alg:TranslateRiver}
    \color{blue}
    \textbf{Input:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs \\

@@

    \color{blue}
    \textbf{Input:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs \\

>>>>

\begin{algorithm}[tb!]
    \caption{Procedure to adjust river positions, remove node overlap and prevent nodes from crossing rivers.}\label{alg:UpdateLayout}
    \textbf{Global variables:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs with the following properties: \\
    \-\hspace{1em}  $\nodeListCross \gets $ the number of $ \node $ in $ \nodeList $ that crosses a river \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    $ \riverList \gets $ a list of $ \river $ representing river features \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

@@

    \begin{algorithmic}[1]
        \Procedure{UpdateLayout}{}
        \While{$ \nodeSize < \nodeSizeMax $}
            \State $ \nodeListCross \gets 1 $ \Comment{Trigger the while loop}
            \While{$ \nodeListCross > 0 $}

                \State $ \nodeListCross \gets 0 $
                \State $ \nodeList \gets $ RemoveOverlap ($ \nodeList $)
                \State \Call{TranslateRiver}{$ \nodeList $}
                \State $\nodeListCross \gets $ \Call{TranslateNode}{$ \nodeList $}

@@

\begin{algorithm}[tb!]
    \caption{Procedure to translate rivers.}\label{alg:TranslateRiver}
    \textbf{Input:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs \\

@@

    \textbf{Input:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs \\
